Evaluating Distance Densities

### 2019-06-06 Scripts/comparing_distance_profiles_using_boxplots.Rmd
edits from tuning mtry

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  whole_genome_dat <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/gm12878_10kb.rds")

	  binslist_dat <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/binslist10.rds")

@@

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  whole_genome_dat <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/gm12878_25kb.rds")

	  binslist_dat <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/binslist25.rds")

@@

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  whole_genome_dat <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/gm12878_50kb.rds")

	  binslist_dat <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/binslist50.rds")

@@

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  whole_genome_dat <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/gm12878_100kb.rds")

	  binslist_dat <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/binslist100.rds")

@@

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  whole_genome_dat <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/K562_10kb.rds")

	  binslist_dat <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/binslist10.rds")

@@

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  whole_genome_dat <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/K562_25kb.rds")

	  binslist_dat <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/binslist25.rds")

@@

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  whole_genome_dat <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/K562_50kb.rds")

	  binslist_dat <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/binslist50.rds")

@@

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  whole_genome_dat <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/K562_100kb.rds")

	  binslist_dat <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/binslist100.rds")

>>>>

whole_genome_dat <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/gm12878_10kb.rds")
binslist_dat <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/binslist10.rds")

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){

@@

```{r}
whole_genome_dat <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/gm12878_25kb.rds")
binslist_dat <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/binslist25.rds")

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){

@@

```{r}
whole_genome_dat <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/gm12878_50kb.rds")
binslist_dat <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/binslist50.rds")

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){

@@

```{r}
whole_genome_dat <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/gm12878_100kb.rds")
binslist_dat <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/binslist100.rds")

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){

@@

```{r}
whole_genome_dat <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/K562_10kb.rds")
binslist_dat <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/binslist10.rds")

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){

@@

```{r}
whole_genome_dat <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/K562_25kb.rds")
binslist_dat <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/binslist25.rds")

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){

@@

```{r}
whole_genome_dat <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/K562_50kb.rds")
binslist_dat <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/binslist50.rds")

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){

@@

```{r}
whole_genome_dat <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/K562_100kb.rds")
binslist_dat <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/binslist100.rds")

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){

### 2019-06-06 Scripts/evaluating_dist_densities.Rmd
edits from tuning mtry

```{r}
NTdistance_list_gm12878 <- readRDS("Z:/TAD_data_analysis/NTdistance_list_gm12878.rds")

LTdistance_list_gm12878 <- readRDS("Z:/TAD_data_analysis/LTdistance_list_gm12878.rds")

@@

```{r}
NTdistance_list_K562 <- readRDS("Z:/TAD_data_analysis/NTdistance_list_K562.rds")

LTdistance_list_K562 <- readRDS("Z:/TAD_data_analysis/LTdistance_list_K562.rds")

@@

###GM12878
```{r}
allplots_gm12878 <- ggarrange(ntplot10kb_gm12878,
                          ntplot25kb_gm12878,
                          ntplot50kb_gm12878,
                          ntplot100kb_gm12878, 
          ncol=4, 
          nrow=1,
          labels = c("A", "B", "C", "D"),
          font.label = list(size=20))
allplots_gm12878
annotate_figure(allplots_gm12878,
                bottom = text_grob("Distance (in millions of basepairs)", 
                                   color = "black", 
                                   face = "bold", 
                                   size = 15),
                left = text_grob("Density", 
                                 color = "black",
                                 size = 15,
                                 rot = 90))

allplots_gm12878 <- ggarrange(ltplot10kb_gm12878,
                          ltplot25kb_gm12878,
                          ltplot50kb_gm12878,
                          ltplot100kb_gm12878, 
          ncol=4, 
          nrow=1,
          labels = c("E", "F", "G", "H"),
          font.label = list(size=20))
allplots_gm12878
annotate_figure(allplots_gm12878,
                bottom = text_grob("Log2 Transformed Distance", 
                                   color = "black", 
                                   face = "bold", 
                                   size = 15),
                left = text_grob("Density", 
                                 color = "black",
                                 size = 15,
                                 rot = 90))

@@

```{r}
allplots_K562 <- ggarrange(ntplot10kb_K562,
                          ntplot25kb_K562,
                          ntplot50kb_K562,
                          ntplot100kb_K562, 
          ncol=4, 
          nrow=1,
          labels = c("A", "B", "C", "D"),
          font.label = list(size=20))
allplots_K562
annotate_figure(allplots_K562,
                bottom = text_grob("Distance (in millions of basepairs)", 
                                   color = "black", 
                                   face = "bold", 
                                   size = 15),
                left = text_grob("Density", 
                                 color = "black",
                                 size = 15,
                                 rot = 90))

allplots_K562 <- ggarrange(ltplot10kb_K562,
                          ltplot25kb_K562,
                          ltplot50kb_K562,
                          ltplot100kb_K562, 
          ncol=4, 
          nrow=1,
          labels = c("E", "F", "G", "H"),
          font.label = list(size=20))
allplots_K562
annotate_figure(allplots_K562,
                bottom = text_grob("Log2 Transformed Distance", 
                                   color = "black", 
                                   face = "bold", 
                                   size = 15),
                left = text_grob("Density", 
                                 color = "black",
                                 size = 15,
                                 rot = 90))

>>>>

```{r}
NTdistance_list_gm12878 <- readRDS("Z:/TAD_data_analysis/distance_densities/NTdistance_list_gm12878.rds")

LTdistance_list_gm12878 <- readRDS("Z:/TAD_data_analysis/distance_densities/LTdistance_list_gm12878.rds")

@@

```{r}
NTdistance_list_K562 <- readRDS("Z:/TAD_data_analysis/distance_densities/NTdistance_list_K562.rds")

LTdistance_list_K562 <- readRDS("Z:/TAD_data_analysis/distance_densities/LTdistance_list_K562.rds")

@@

###GM12878
```{r}

gm12878_nt_plot <- ggplot(gm12878_dist_densities[which(gm12878_dist_densities$Transformation=="Untransformed"),], aes(x=value, group=variable)) + 
  facet_grid(Transformation ~ Resolution, scales="free") +
  geom_density(alpha=.5, color="red") + 
  xlim(0,30000000) +
  scale_x_continuous(limits = c(0,3e+7),
                     breaks = c(0, 1e+07, 2e+07, 3e+07),
                     labels = c(0,1,2,3))+
  xlab("") + ylab("") +
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_text(size=15),
     axis.text.y = element_blank(),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     strip.text.x = element_text(size = 15),
     strip.text.y = element_text(size = 15),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

gm12878_lt_plot <- ggplot(gm12878_dist_densities[-which(gm12878_dist_densities$Transformation=="Untransformed"),], aes(x=value, group=variable)) + 
  facet_grid(Transformation ~ Resolution, scales="free") +
  geom_density(alpha=.5, color="blue") + 
  xlab("") + ylab("") +
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_text(size=15),
     axis.text.y = element_blank(),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     strip.text.x = element_text(size = 15),
     strip.text.y = element_text(size = 15),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

allplots_gm12878 <- ggarrange(gm12878_nt_plot,
                          gm12878_lt_plot, 
          ncol=1, 
          nrow=2,
          labels = "AUTO",
          font.label = list(size=20))
allplots_gm12878
annotate_figure(allplots_gm12878,
                bottom = text_grob("Distance (mb)", 
                                   color = "black", 
                                   face = "bold", 
                                   size = 15),
                left = text_grob("Density", 
                                 color = "black",
                                 size = 15,
                                 rot = 90))
```

@@

```{r}
K562_dist_densities <- rbind.data.frame(NTdistance_list_K562[[1]],
                                           NTdistance_list_K562[[2]],
                                           NTdistance_list_K562[[3]],
                                           NTdistance_list_K562[[4]],
                                           LTdistance_list_K562[[1]],
                                           LTdistance_list_K562[[2]],
                                           LTdistance_list_K562[[3]],
                                           LTdistance_list_K562[[4]])
K562_dist_densities$Transformation <- c(rep("Untransformed", dim(NTdistance_list_K562[[1]])[1] + 
                                                                dim(NTdistance_list_K562[[2]])[1] +
                                                                dim(NTdistance_list_K562[[3]])[1] +
                                                                dim(NTdistance_list_K562[[4]])[1]),
                                           rep("Log2 Transformed", dim(LTdistance_list_K562[[1]])[1] + 
                                                                dim(LTdistance_list_K562[[2]])[1] +
                                                                dim(LTdistance_list_K562[[3]])[1] +
                                                                dim(LTdistance_list_K562[[4]])[1]))
K562_dist_densities$Resolution <- c(rep("10 kb", dim(NTdistance_list_K562[[1]])[1]),
                                       rep("25 kb", dim(NTdistance_list_K562[[2]])[1]),
                                       rep("50 kb", dim(NTdistance_list_K562[[3]])[1]),
                                       rep("100 kb", dim(NTdistance_list_K562[[4]])[1]),
                                       rep("10 kb", dim(LTdistance_list_K562[[1]])[1]),
                                       rep("25 kb", dim(LTdistance_list_K562[[2]])[1]),
                                       rep("50 kb", dim(LTdistance_list_K562[[3]])[1]),
                                       rep("100 kb", dim(LTdistance_list_K562[[4]])[1]))
K562_dist_densities$Transformation <- factor(K562_dist_densities$Transformation, levels=c("Untransformed", "Log2 Transformed"))
K562_dist_densities$Resolution <- factor(K562_dist_densities$Resolution, levels=c("10 kb", "25 kb", "50 kb", "100 kb"))

K562_nt_plot <- ggplot(K562_dist_densities[which(K562_dist_densities$Transformation=="Untransformed"),], aes(x=value, group=variable)) + 
  facet_grid(Transformation ~ Resolution, scales="free") +
  geom_density(alpha=.5, color="red") + 
  xlim(0,30000000) +
  scale_x_continuous(limits = c(0,3e+7),
                     breaks = c(0, 1e+07, 2e+07, 3e+07),
                     labels = c(0,1,2,3))+
  xlab("") + ylab("") +
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_text(size=15),
        axis.text.y = element_blank(),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        strip.text.x = element_text(size = 15),
        strip.text.y = element_text(size = 15),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20))

K562_lt_plot <- ggplot(K562_dist_densities[-which(K562_dist_densities$Transformation=="Untransformed"),], aes(x=value, group=variable)) + 
  facet_grid(Transformation ~ Resolution, scales="free") +
  geom_density(alpha=.5, color="blue") + 
  xlab("") + ylab("") +
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_text(size=15),
        axis.text.y = element_blank(),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        strip.text.x = element_text(size = 15),
        strip.text.y = element_text(size = 15),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20))

allplots_K562 <- ggarrange(K562_nt_plot,
                              K562_lt_plot, 
                              ncol=1, 
                              nrow=2,
                              labels = "AUTO",
                              font.label = list(size=20))
allplots_K562
annotate_figure(allplots_K562,
                bottom = text_grob("Distance (mb)", 
                                   color = "black", 
                                   face = "bold", 
                                   size = 15),
                left = text_grob("Density", 
                                 color = "black",
                                 size = 15,
                                 rot = 90))
```
